---
title: "Bednet"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Bed nets in malaria simulation

For each aspect of net distribution, state if the average population usage will increase or decrease:

```{r malarisimulation-dist}
quiz(
  question("More frequent distributions",
           answer("Increase", correct = TRUE),
           answer("Decrease")
  ),
  question("Larger distributions",
           answer("Increase", correct = TRUE),
           answer("Decrease")
  ),
  question("Shorter retention halflife",
           answer("Increase"),
           answer("Decrease", correct = TRUE)
  ),
  question("3-yearly mass distributions versus annual continuous distribution",
           answer("Increase"),
           answer("Decrease"),
           answer("It depends!", correct = TRUE)
  )
)
```

## Fitting malariasimulation inputs

Consider the following scenario:

-   Time period: 10 years (time units are days so, for year one: t = 1:365)
-   Bed net usage estimates of 12%, 18%, 45%, 50% and 40%, collected at the mid point of the year (1st June) in years 1, 3, 5, 7, and 9
-   Known mass net distributions at the start of the year (1st January) in years 1, 2, 4, 7 and 8.
-   Net retention half life of 5 years

Using these estimates and the `netz::fit_usage()` function, in the code box below estimate the model input distribution to achieve the observed bed net usage over time.

```{r estimate-dist, exercise=TRUE}
library(netz)

```

```{r estimate-dist-solution}
library(netz)
year <- 365
timesteps <- 10 * year
net_hl <- 5 * year

# Target usage associated time points
target <- c(0.12, 0.18, 0.45, 0.50, 0.40)
target_tt <- floor((c(1, 3, 5, 7, 9) - 0.5) * year)
# Time points at which distribution will occur
distribution_tt <- 1 + c(0, 1, 3, 6, 7) * year

# Fit
fit <- netz::fit_usage(
  target_usage = target,
  target_usage_timesteps = target_tt,
  distribution_timesteps = distribution_tt + 1
)

round(fit$par, 2)
```

With your estimated inputs and the `netz::population_usage()` function, plot the estimated usage over time alongside the usage observations.

```{r plot-dist, exercise=TRUE}
library(netz)

```

```{r plot-dist-solution}
library(netz)

# Our estimates of the distributions
fitted_input <- c(0.13, 0.15, 0.53, 0.33, 0.16)

year <- 365
timesteps <- 10 * year
net_hl <- 5 * year

# Target usage associated time points
target <- c(0.12, 0.18, 0.45, 0.50, 0.40)
target_tt <- floor((c(1, 3, 5, 7, 9) - 0.5) * year)
# Time points at which distribution will occur
distribution_tt <- 1 + c(0, 1, 3, 6, 7) * year
# Estimate population usage over time
pu <- population_usage(
  timesteps = timesteps,
  distribution = fitted_input,
  distribution_timesteps = distribution_tt,
  half_life = net_hl)
# Plot the results against the target
plot(1:timesteps, pu, t = "l", ylim = c(0, 0.8), ylab = "Population usage", xlab = "Time")
points(target ~ target_tt, col = "dodgerblue", pch = 19)
```

`r emo::ji("question")` Are they a good match?

Extra credits `r emo::ji("sparkles")`:

-   Examine the `distribution_upper` argument of `netz::fit_usage()`. How does the fit look if you limit the maximum a single distribution can be to 40% of the population?
-   We may be uncertain about the net distribution dates. Do other sets of distribution dates also allow a good fit to the observed bed net usage estimates?

## Working with country net data

When working with country net data there are various bed net metrics that you might encounter.

Match the following definitions and metrics:

```{r metric-def}
quiz(
  question("The total number of nets in the population",
           answer("Distribution"),
           answer("Crop", correct = TRUE),
           answer("Access"),
           answer("Usage")
  ),
  question("The proportion of people who have slept under a bed net the previous night",
           answer("Distribution"),
           answer("Crop"),
           answer("Access"),
           answer("Usage", correct = TRUE)
  ),
  question("The number of nets distributed",
           answer("Distribution", correct  = TRUE),
           answer("Crop"),
           answer("Access"),
           answer("Usage")
  ),
  question("The proportion of the population that could sleep under a net",
           answer("Distribution"),
           answer("Crop"),
           answer("Access", correct = TRUE),
           answer("Usage")
  )
)
```

Using the `netz::get_usage_rate_data()`, `netz::access_to_usage()` and `netz::usage_to_access()` functions, use the code box below to generate answers to the following questions

```{r access-usage, exercise=TRUE}
library(netz)

```

```{r access-usage-quiz}
quiz(
  question("What is the usage rate in Nigeria?",
           answer("0.9376562"),
           answer("0.8901211"),
           answer("0.8795992", correct = TRUE),
           answer("0.6942281")
  ),
  question("What is the usage in Burkina Faso if access is 62%",
           answer("0.5537472", correct = TRUE),
           answer("0.6494372"),
           answer("0.4328341"),
           answer("0.5100225")
  ),
  question("Which country uses accessible nets most efficiently?",
           answer("Zambia"),
           answer("Tanzania"),
           answer("Scotland", message = "Time for coffee I think!"),
           answer("Benin", correct = TRUE)
  )
)
```

Can you work out the annual cost for the following scenario:

-   Annual distributions
-   Cost per net delivered of \$5
-   Population size of 10,000
-   Net loss half life of 2.5 years, net loss retention function: `net_loss_map()`
-   Usage of 70% and usage rate of 0.8

The [netz flow diagram](https://mrc-ide.github.io/netz/) might help

```{r net-cost, exercise=TRUE}
library(netz)

```

```{r net-cost-hint}
library(netz)
population <- 10000
cost_per_net_delivered <- 5
year <- 365
distribution_freq <- 1 * year
retention_half_life <- 2.5 * year
net_loss_function <- net_loss_map
usage <- 0.7
usage_rate <- 0.8

# Now use the netz conversion functions to translate
# usage -> access -> crop -> distribution
```

```{r net-cost-solution}
library(netz)
population <- 10000
cost_per_net_delivered <- 5
year <- 365
distribution_freq <- 1 * year
retention_half_life <- 2.5 * year
net_loss_function <- net_loss_map
usage <- 0.7
usage_rate <- 0.8

access <- netz::usage_to_access(usage, usage_rate)
crop <- netz::access_to_crop(access)
nets_distributed_per_capita <- netz::crop_to_distribution(crop, distribution_freq, retention_half_life, net_loss_function)
nets_distributed <- nets_distributed_per_capita * population
cost <- nets_distributed * cost_per_net_delivered
cost
```
