---
title: "Calibration"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## When to calibrate

Let's start with a quiz to explore possible situations where you might face the decision of whether to calibrate or not

```{r quiz}
quiz(
  question("I've edited the historical bednet coverage, I need to...",
           answer("re-calibrate", correct = TRUE),
           answer("run the site as is")
  ),
  question("I want to use a site file out of the box from the site package, should I...",
           answer("calibrate"),
           answer("not calibrate"),
           answer("check if I need to update the inputs then decide", correct = TRUE)
  ),
  question("There has been an update to the parameterisation of bednets and all of my sites have historical bed net usage. I should",
           answer("re-calibrate all sites", correct = TRUE),
           answer("ignore it and hope the problem goes away")
  ),
  question("I'm running five different future scenarios for my site, each with different prospective intervention coverage. Do I need to recalibrate the site for each scenario? ",
           answer("yes"),
           answer("no", correct = TRUE)
  )
)
```

## The summary function

When running `calibrate()` we must provide a summary function that summarised the raw simulation output in the same format as our target.

1.  In the code box below, compete the summary function, to match the format of our target data.

```{r summary-function, exercise=TRUE}
# Target: all age clinical incidence (cases per person per year) in years 2, 3 and 4
target <- c(0.03, 0.02, 0.01)
# Raw simulation output
simulation <- data.frame(
  timestep = 1:(365 * 5),
  n = 10000,
  cases = rpois(365 * 5, 200 / 365)
)
# Summary function
summary_function <- function(simulation){
  
}
summary_function(simulation)
```

```{r summary-function-hint}
# Summary function - estimate annual incidence in years 2-4
summary_function <- function(simulation){
  year <- ceiling(simulation$timestep / 365)
  annual_inc <- tapply(simulation$cases, year, sum) / 10000
  return(annual_inc[2:4])
}
```

## Calibrate good times, come on `r emo::ji("popper")`

In the following code box we can run a simple calibration.

1.  Work through the code in the box to make sure you understand what each section is doing.

2.  When you're happy hit run to perform the calibration. Remember, calibration takes multiple model-runs so won't be instant (this example is artificially set up to run reasonably quickly).

After the calibration finishes you'll see a print out summarising the attempted EIR and comparisons between the summarised model output and target.

```{r calibration, exercise=TRUE, exercise.timelimit=1200}
library(malariasimulation)
library(cali)

# Define our target. In this example we have a PfPr estimate for year 3
target_pfpr <- 0.3

# Define our simulation parameters, we need to add $timesteps for the calibration
p <- malariasimulation::get_parameters(
  overrides = list(
    human_population = 5000,
    individual_mosquitoes = FALSE
  )
)
p$timesteps <- 3 * 365

# Write our summary function. To match the target we need to
# output average PfPr in year 3
get_pfpr_year_3 <- function(simulation_output){
  year3 <- simulation_output[simulation_output$timestep > 2 * 365,]
  pfpr <- year3$n_detect_730_3650 / year3$n_730_3650
  average_pfpr <- mean(pfpr)
  return(average_pfpr)
}

# Run a test simulation to check our target function does what it should!
simulation <- malariasimulation::run_simulation(
  timesteps = p$timesteps,
  parameters = p
)
# Does this look right? Does it match the type of target data?
get_pfpr_year_3(simulation)

# When we are happy we can run the calibration
set.seed(1234)
calibration <- cali::calibrate(target = target_pfpr,
                summary_function = get_pfpr_year_3,
                parameters = p,
                tolerance = 0.005,
                low = 1, high = 10)

message("Calibrated EIR estimate: ", calibration)
```

Lets check our results:

1.  Use the estimated, calibrated EIR from above to modify our parameter inputs
2.  Plot simulated PfPr over time
3.  Add your target.

`r emo::ji("question")` Do they match?

```{r calibration-check, exercise=TRUE, exercise.timelimit=1200}
target_pfpr <- 0.3

# Set the initial parameters
calibrated_p <- malariasimulation::get_parameters(
  overrides = list(
    human_population = 5000,
    individual_mosquitoes = FALSE
  )
)
calibrated_p$timesteps <- 3 * 365

# Set the initial EIR (Add your calibrated estimate here)
calibrated_p <- calibrated_p |>
  malariasimulation::set_equilibrium(init_EIR = )

set.seed(1234)
calibrated_simulation <- malariasimulation::run_simulation(
  timesteps = calibrated_p$timesteps,
  parameters = calibrated_p
)
```

```{r calibration-check-hint, exercise.timelimit=1200}
# Set the initial EIR (Add your calibrated estimate here)
calibrated_p <- calibrated_p |>
  malariasimulation::set_equilibrium(init_EIR = 4.216965)

# Plotting output
calibrated_prev <- calibrated_simulation$n_detect_730_3650 / calibrated_simulation$n_730_3650
year <- calibrated_simulation$timestep / 365

plot(NA, xlim = c(0, 3), ylim = c(0, 0.8),
     xlab = "Year", ylab = "PfPr")
segments(x0 = 2, y0 = target_pfpr, x1 = 3, y1 = target_pfpr, col = "red", lwd = 4)
lines(calibrated_prev ~ year)
```

Extra credits `r emo::ji("sparkles")`:

-   Modify the calibration code to calibrate to 3 years of target data.
-   Read about the `weights` argument in `?calibrate()`, have a go a weighting your target data so more recent years are more influential.

`r emo::ji("question")` What happens if you change the `tolerance` argument in `?calibrate()`
