---
title: "Introduction"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Exploring a site file

Let's start by getting better acquainted with a country site file. In the code box below we have pre-loaded the site for Togo (iso3c = TGO).

Use the interactive code box below to explore the elements that make up the site file.

1.  Choose to explore specific elements of a list with the `$` operator. For example `togo_site_file$seasonality` or `togo_site_file$prevalence` . You can see all the elements with `names(togo_site_file)`. It may be helpful to plot some elements to see what is going on.
2.  Dig into the `togo_site_file` details to answer the questions below. Remember, you can find out more information about site file elements on the [foresite website](https://mrc-ide.github.io/foresite/).

```{r explore-a-site, exercise=TRUE}
library(foresite)
togo_site_file <- TGO

```

```{r quiz}
quiz(
  question("What is the PfPr prevalence in the iso3c = TGO, name_1 = Centre, urban_rural = rural in 2005?",
           answer("0"),
           answer("0.2459082"),
           answer("0.5470634", correct = TRUE),
           answer("0.8")
  ),
  question("What is the dominant vector species in iso3c = TGO, name_1 = Kara",
           answer("arabiensis"),
           answer("funestus"),
           answer("gambiae", correct = TRUE)
  ),
  question("Did the World Malaria Report estimate a rise or fall in malaria cases in Togo 
           between 2019 and 2020",
           answer("Rise", correct = TRUE),
           answer("Fall")
  )
)
```

## Extracting a single site

Each country site file contains multiple sites. In our case these are sub-national units where the population is further disaggregated spatially and by the urban/rural distinction. We can use the helper function `site::single_site()` to extract information for a single site (sub-national unit) from the country site file.

To find out which site to index we can look up all of the sites within a country with `$sites`.

By editing the code below:

1.  Isolate the site iso3c = TGO, name_1 = Savanes urban_rural = rural

2.  Plot the estimated bed net usage for that site over time

3.  Examine your plot to answer the question below

```{r single-site, exercise=TRUE}
library(foresite)
library(site)
togo_site_file <- TGO

```

```{r single-site-solution}
library(foresite)
library(site)
togo_site_file <- TGO
togo_site_file$sites
savanes_rural <- single_site(togo_site_file, 9)
plot(savanes_rural$interventions$itn_use ~ savanes_rural$interventions$year, t = "l")
```

```{r quiz2}
quiz(
  question("In what year did itn use in iso3c = TGO, name_1 = Savanes, urban_rural = rural first exceed 50%?",
           answer("2000"),
           answer("2011", correct = TRUE),
           answer("2012"),
           answer("2015")
  )
)
```

## Running a single site

Now lets try running a site.

1.  Use the `site::single_site()` function to isolate the site for: Run iso3c = TGO, name_1 = Plateaux, urban_rural = rural.

2.  Create a `r emo::ji("package")` malariasimulation parameter list using the `site::site_parameters()` function. For today, in the `overrides` argument you might want to set a reasonably small population so that the model runs quickly, for example `overrides  = list(human_population = 5000)`.

3.  Run the site using `malariasimulation::run_simulation()`

4.  Plot the *Pf*Pr~2-10~ estimated by the model

5.  Overlay the Malaria Atlas Project estimates of *Pf*Pr~2-10~ onto your plot.

`r emo::ji("warning")` The model run may take a little while to complete (\~5 mins). While you wait, why not have a look at the [foresite website](https://mrc-ide.github.io/foresite/), or starting thinking through the [coffee break activity](https://mrc-ide.github.io/mvw/coffee.html) `r emo::ji("warning")`

```{r run-site, exercise=TRUE, exercise.timelimit=1200}
library(foresite)
library(site)
library(malariasimulation)
togo_site_file <- TGO

```

```{r run-site-solution}
library(foresite)
library(site)
library(malariasimulation)
togo_site_file <- TGO
# Isolate the site
site_index <- which(togo_site_file$sites$name_1 == "Plateaux" &
                      togo_site_file$sites$urban_rural == "rural")
plateaux_rural <- single_site(togo_site_file, site_index)
# Create parameter inputs
site_pars <- site_parameters(
  interventions = plateaux_rural$interventions,
  demography = plateaux_rural$demography,
  vectors = plateaux_rural$vectors,
  seasonality = plateaux_rural$seasonality,
  eir = plateaux_rural$eir$eir[1],
  overrides = list(human_population = 5000)
)
# Run!
model_run <- run_simulation(timesteps = site_pars$timesteps,
                            parameters = site_pars)
# Calculate prevalence
model_run$prevalence <- model_run$n_detect_730_3649 / model_run$n_730_3649
# Set the time
model_run$t <- (model_run$timestep / 365) + 2000
# Plot
plot(model_run$prevalence ~ model_run$t, t = "l", ylim = c(0, 0.8), xlab = "Year", ylab = "Prevalence")
# Add MAP prevalence
points(plateaux_rural$prevalence$year + 0.5, plateaux_rural$prevalence$pfpr, pch = 19, col = "darkred")
```

`r emo::ji("question")` How well do they match?

`r emo::ji("question")` Why might there be differences between modelled *Pf*Pr~2-10~ and the estimates from the Malaria Atlas Project?

Extra credits `r emo::ji("sparkles")`:

-   Try changing the EIR argument in `site_parameters()`
-   Modify `plateaux_rural$interventions$irs_cov` and re-run, can you see the impact?
-   Try running multiple different sites and estimating aggregated *Pf*Pr~2-10~ across all of them.
